### 2021-12-07 input/proposal.tex
not much

\begin{definition}[Autonomous systems]
  An autonomous system is a network comprising nodes and communication
  links that we represent as a \underline{g}raph of
  \underline{v}ertices and \underline{e}dges:
  $G = \langle V, E \rangle$ with $E \in V \times V$. A
  \underline{p}ath $\pi_{xz}$ from \Process~$x$ to \Process~$z$ is a
  sequence of contiguous edges
  $[\langle x, y_1 \rangle, \langle y_1, y_2\rangle, \ldots, \langle
  y_n, z \rangle]$.
\end{definition}

@@

Unfortunately, \processes do not share a common global knowledge of
the network state. For \processes to eventually ($\eventually$) reach
consistent partitioning, each source $s$ must send
\texttt{\underline{A}dd} notifications $\alpha_s$ to all \processes
that are closer to it than any other source, along with enough
metadata to allow them to decide of their closest source. A simple
implementation consists in ensuring that each \process $x$ eventually
receives $\alpha_s^{|\Pi_{sx}|}$ where $\Pi_{sx}$ is the \emph{best}
path from any source to it; the value $|\Pi_{sx}|$ being built over
forwarding along this path.

@@

\begin{algorithm}
  \input{input/algoadd.tex}
  \caption{\label{algo:add}Adding a partition by \Process~$p$.}
\end{algorithm}

@@

\begin{definition}[\label{def:dcp}\underline{D}ynamic
  \underline{c}onsistent \underline{p}artitioning (DCP)]
  Dynamic consistent partitioning is consistent partitioning where
  \processes can join or leave the set of sources at any \TODO{time}.
\end{definition}

@@

@@

\begin{definition}[\label{def:fbplus}FB$^+$: echos] FB where a
  \process $x$ that receives a staleness notification sends back --~or
  echoes~-- its best up-to-date delivered message: $r_{xy}(\alpha_s)
  \wedge \delta_s \in D_x \implies s_{xy}(\alpha_{s'})$ with
  $\alpha_{s'} = \min D_x \wedge \delta_{s'} \not\in
  D_x$. \TODO{Rework min}
\end{definition}

\TODO{Naive implementation is FB$^+$ etc. It does not work.}

\begin{lemma}[\label{lem:fbfse}FB$^+ \wedge$ FS $\centernot\implies$ DCP]
  Forwarding best up-to-date, forwarding staleness, and echoing is not
  sufficient to guarantee dynamic consistent partitioning.
\end{lemma}

@@

\begin{algorithm}
  \input{input/algoascast.tex}
  \caption{\label{algo:ascast}\NAME at \Process~$p$.}
\end{algorithm}

>>>>

\begin{definition}[Autonomous system]
  An autonomous system is a network comprising nodes and communication
  links that we represent as a \underline{g}raph of
  \underline{v}ertices and \underline{e}dges:
  $G = \langle V, E \rangle$ with $E \in V \times V$. A
  \underline{p}ath $\pi_{xz}$ from \Process~$x$ to \Process~$z$ is a
  sequence of contiguous edges
  $[\langle x, y_1 \rangle, \langle y_1, y_2\rangle, \ldots, \langle
  y_n, z \rangle]$.
\end{definition}

@@

Unfortunately, \processes do not share a common global knowledge of
the network state. For \processes to eventually ($\eventually$) reach
consistent partitioning, each source $s$ must send
\texttt{\underline{A}dd} notifications $\alpha_s$ to all \processes
that are closer to it than any other source, along with enough
metadata to allow them to decide of their closest source. A simple
implementation based on Definition~\ref{def:scoped} consists in
ensuring that each \process $x$ eventually receives
$\alpha_s^{|\Pi_{sx}|}$ where $\Pi_{sx}$ is the \emph{best} path from
any source to it; the value $|\Pi_{sx}|$ being built over forwarding
along this path.

@@

\begin{algorithm}
  \input{input/algoadd.tex}
  \caption{\label{algo:add}Add-only CP protocol at \Process~$p$.}
\end{algorithm}

@@

\begin{definition}[\label{def:dcp}\underline{D}ynamic
    \underline{c}onsistent \underline{p}artitioning (DCP)] A DCP
  protocol enables \processes to join or leave the set of sources at
  any time while ensuring eventual consistent partitioning.
  % Dynamic consistent partitioning is consistent partitioning where
  % \processes can join or leave the set of sources at any \TODO{time}.
\end{definition}

@@

%% Unfortunately, depending on receipt order of messages, \processes may
%% converge to

@@

\begin{definition}[\label{def:fbplus}$\textup{FB}^+$: echos] FB where a
  \process $x$ that receives a staleness notification sends back --~or
  echoes~-- its best up-to-date delivered message: $r_{xy}(\alpha_s)
  \wedge \delta_s \in D_x \implies s_{xy}(\alpha_{s'})$ with
  $\alpha_{s'} = \min D_x \wedge \delta_{s'} \not\in
  D_x$. \TODO{Rework min}
\end{definition}

\TODO{The naive implementation described above is $\textup{FB}^+
  \wedge FS$. And it does  not work.}

\begin{lemma}[\label{lem:fbfse}$\textup{FB}^+ \wedge \textup{FS}
    \centernot\implies \textup{DCP}$] Forwarding best up-to-date,
  forwarding staleness, and echoing is not sufficient to guarantee
  dynamic consistent partitioning.
\end{lemma}

@@

\begin{algorithm}
  \input{input/algoascast.tex}
  \caption{\label{algo:ascast}\NAME: DCP protocol at \Process~$p$.}
\end{algorithm}
